Forecasting short-term hourly Emergency Departement arrivals

### 2021-11-02 paper/paper.Rmd

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggplot2)
library(RColorBrewer)
library(ggridges)
library(hrbrthemes)
library(ggthemes)
library(scales)
library(ggtext)
library(extrafont)
```

@@

(Plots generated with theme_few - they look nice, good suggestion! Not sure how to include them in bookdown, can you help, Bahman? The plots are in the results folder for now, can either point to them from here, or I can change the Evauation script to save them somewhere else, and maybe in a different format? I guess PDF might be preferred. I realise that while I prepared my secript to produce point forecasts I haven't run it yet so will do this next week.)

@@

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=FALSE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggplot2)
library(RColorBrewer)
library(ggridges)
library(hrbrthemes)
library(ggthemes)
library(scales)
library(ggtext)
library(extrafont)
```

@@

@@

```{r time-accuracy, fig.cap= "Running time ...", fig.align='center',out.width= "70%"}
```

### 2021-11-02 paper/paper.tex

(Plots generated with theme\_few - they look nice, good suggestion! Not sure how to include them in bookdown, can you help, Bahman? The plots are in the results folder for now, can either point to them from here, or I can change the Evauation script to save them somewhere else, and maybe in a different format? I guess PDF might be preferred. I realise that while I prepared my secript to produce point forecasts I haven't run it yet so will do this next week.)

@@

\caption{\label{tab:tab-results}Summary of studies in hourly emergency care forecasting}
\centering
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{lrrr}
\toprule
Method & Quantile Bias & Pinball & RMSE\\
\midrule
Benchmark-1 & 0.1047874 & 1.254491 & NA\\
Benchmark-2 & 0.0557392 & 1.217429 & NA\\
ETS(XXX) & 0.0194389 & 1.434862 & 0.0121247\\
GBM & 0.0600650 & 1.263135 & NA\\
NBI-2-I & 0.0540740 & 1.206238 & NA\\
NBI-2-log & 0.0375705 & 1.188041 & NA\\
NOtr-1 & 0.0098936 & 1.222584 & NA\\
NOtr-2 & 0.0118522 & 1.208556 & NA\\
Poisson-1 & 0.0372137 & 1.204936 & NA\\
Poisson-2 & 0.0373884 & 1.188107 & NA\\
Poisson-2-I & 0.0523937 & 1.222114 & NA\\
RegressionPoisson & 0.0929416 & 1.293524 & 0.8490258\\
Ttr-2 & 0.0140252 & 1.210105 & NA\\
faster & 0.1862190 & 35.051012 & NA\\
iETSCeiling & 0.0104673 & 1.419490 & NA\\
iETSXSeasonal & 0.0104673 & 1.417260 & 0.0896228\\
qreg-1 & 0.0643451 & 1.340557 & NA\\
tbats & 0.0855702 & 1.536080 & 0.4859770\\
\bottomrule
\end{tabular}
\end{table}

@@

>>>>

@@

\caption{\label{tab:tab-results}Summary of studies in hourly emergency care forecasting}
\centering
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{lrrrr}
\toprule
Method & Quantile Bias & Pinball & RMSE & Time\\
\midrule
ADAM-iETSX & 0.0104673 & 1.417260 & 0.0896228 & 92.9348605\\
ADAM-iETSX-Ceiling & 0.0104673 & 1.419490 & NA & NA\\
Benchmark-1 & 0.1047874 & 1.254491 & 1.0042634 & 0.3874450\\
Benchmark-2 & 0.0557392 & 1.217429 & 0.2592800 & 0.0947247\\
ETS & 0.0194389 & 1.434862 & 0.0121247 & 10.7175205\\
GBM-2 & 0.0600153 & 1.261690 & 1.7770897 & 602.4317496\\
LinearRegression & NA & NA & NA & 3.1543500\\
NBI-2 & 0.0540725 & 1.206241 & 0.3830272 & NA\\
NOtr-1 & 0.0098967 & 1.222583 & 0.2675957 & 451.6620471\\
NOtr-2 & 0.0118522 & 1.208561 & 0.2675957 & 86.5895462\\
Poisson-1 & 0.0372137 & 1.204920 & 0.0095263 & 1.4763353\\
Poisson-2 & 0.0373884 & 1.188109 & 0.0082932 & 5.0768588\\
Poisson-2-I & 0.0523937 & 1.222114 & 0.3770081 & NA\\
Regression-Poisson & 0.0929416 & 1.293524 & 0.8490258 & 67.1401641\\
Ttr-2 & 0.0140221 & 1.210108 & 0.3324146 & 956.5532849\\
fasster & 0.1862190 & 35.051012 & 127.7504023 & NA\\
prophet & 0.0193799 & 1.447037 & 0.2955460 & 20.6755021\\
qreg-1 & 0.0643451 & 1.340557 & NA & NA\\
tbats & 0.0855702 & 1.536080 & 0.4859770 & 273.0558176\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=0.7\linewidth]{paper_files/figure-latex/time-accuracy-1}

\caption{Running time ...}\label{fig:time-accuracy}
\end{figure}
